DATA 624 Homework 1

### 2020-01-31 DATA624/HW1.Rmd
More work on HW1

---
title: "DATA 624 Homework 1"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth: 3
    code_folding: "show"
---

```{r setup, echo=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(fpp2)
```

## 2.1

@@

@@

@@

@@

## 2.2

@@

```{r}
download.file("http://otexts.com/fpp2/extrafiles/tute1.csv", "tute1.csv")
tute1 <- read.csv("tute1.csv", header=TRUE)
View(tute1)
```

@@

## 2.3

@@

```{r}
download.file("https://otexts.com/fpp2/extrafiles/retail.xlsx", "retail.xlsx")
retaildata <- readxl::read_excel("retail.xlsx", skip=1)
```

@@

@@

## 2.6

@@

@@

@@

>>>>

---
title: "DATA 624 Homework 1"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth: 3
    code_folding: "hide"
---

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(fpp2)
library(gridExtra)
```

## Question 2.1

@@

**`gold` is the daily morning gold prices in US dollars from 1 Jan 1985 to 31 March 1989.  `woolyrnq` is the quarterly production of woolen yarn in Australia in tons from March 1965 to September 1994.  `gas` is monthly gas production in Australia from 1956-1995.**

@@

```{r}
autoplot(gold)
autoplot(woolyrnq)
autoplot(gas)
```

@@

```{r}
frequency(gold)
frequency(woolyrnq)
frequency(gas)
```

@@

```{r}
goldoutlier <- which.max(gold)
```

**It is the `r goldoutlier` observation.  The price of gold was `r gold[goldoutlier]`**

## Queston 2.2

@@

```{r}
if(!file.exists("tute1.csv")){
  download.file("http://otexts.com/fpp2/extrafiles/tute1.csv", "tute1.csv")
}
tute1 <- read.csv("tute1.csv", header=TRUE)
View(tute1)
```

@@

## Question 2.3

@@

```{r}
if(!file.exists("retail.xlsx")){
  download.file("https://otexts.com/fpp2/extrafiles/retail.xlsx", "retail.xlsx")
}
retaildata <- readxl::read_excel("retail.xlsx", skip=1)
```

@@

```{r}
autoplot(myts)
ggseasonplot(myts)
ggsubseriesplot(myts)
gglagplot(myts)
ggAcf(myts)
```

@@

**There is a clear seasonality increase in retail sales from October to the end of the year.  This is the Christmas shopping season.  There is also a trend of increasing retail sales over time.  The trend has been rising untill the 2000's where it flatened out for roughly a decade.  Since 2010 it looks like the trend increases again.**

## Question 2.6

@@

### hsales

@@

```{r}
autoplot(hsales)
ggseasonplot(hsales)
ggsubseriesplot(hsales)
gglagplot(hsales)
ggAcf(hsales)
```

@@

### usdeaths

```{r}
autoplot(usdeaths)
ggseasonplot(usdeaths)
ggsubseriesplot(usdeaths)
gglagplot(usdeaths)
ggAcf(usdeaths)
```

### bricksq

```{r}
autoplot(bricksq)
ggseasonplot(bricksq)
ggsubseriesplot(bricksq)
gglagplot(bricksq)
ggAcf(bricksq)
```

### sunspotarea

```{r}
autoplot(sunspotarea)
#ggseasonplot(sunspotarea)
#ggsubseriesplot(sunspotarea)
gglagplot(sunspotarea)
ggAcf(sunspotarea)
```

### gasoline

```{r}
autoplot(gasoline)
ggseasonplot(gasoline)
#ggsubseriesplot(gasoline)
gglagplot(gasoline)
ggAcf(gasoline)
```
